A Finite Volume Formulation for the 2D Incompressible Navier-Stokes and Conduction Equations

### 2012-07-23 doc/model_problems/model_problems.tex
fixed errors in conduction equation derivation in model problem doc

\begin{multline}
  C_{P_{ij}}( T^{n+1}_{ij} - T^n_{ij} ) = \frac{\Delta_t}{\Delta_i
    \Delta_j} -\beta_{i-1/2,j} \frac{T^{n+1}_{ij}
    -T^{n+1}_{i-1,j}}{\Delta_i} +\beta_{i+1/2,j} \frac{T^{n+1}_{i+1,j}
    -T^{n+1}_{ij}}{\Delta_i}\\
  -\beta_{i,j-1/2} \frac{T^{n+1}_{ij}
    -T^{n+1}_{i,j-1}}{\Delta_j} +\beta_{i,j+1/2} \frac{T^{n+1}_{i,j+1}
    -T^{n+1}_{i,j-1}}{\Delta_j}\:.
  \label{eq:conduction_fv_multline}
\end{multline}

@@

Rearranging for temperature, we can then form a system of equations
amenable to matrix solutions, not yet considering boundary conditions,
arriving at the discrete, time-dependent conduction equation:

\begin{multline}
 \Big[1 + \frac{\alpha_{ij}}{\Delta_i}(\beta_{i-1/2,j} + \beta_{i+1/2,j})\Big]
 T^{n+1}_{ij} + \Big[-\frac{\alpha_{ij}}{\Delta_i} \beta_{i-1/2,j}\Big]
 T^{n+1}_{i-1,j} + \Big[\frac{-\alpha_{ij}}{\Delta_i} \beta_{i+1/2,j}\Big]
 T^{n+1}_{i+1,j}\\
 + \Big[-\frac{\alpha_{ij}}{\Delta_j} \beta_{i-1/2,j}\Big]
 T^{n+1}_{i,j-1} + \Big[-\frac{\alpha_{ij}}{\Delta_j} \beta_{i+1/2,j}\Big]
 T^{n+1}_{i,j+1} = T^n_{ij}\:.
 \label{eq:conduction_inner_terms}
\end{multline}

>>>>

\begin{multline}
  C_{P_{ij}}( T^{n+1}_{ij} - T^n_{ij} ) = \frac{\Delta_t}{\Delta_i
    \Delta_j} -\beta_{i-1/2,j} \frac{T^{n+1}_{ij}
    -T^{n+1}_{i-1,j}}{\Delta_i} +\beta_{i+1/2,j} \frac{T^{n+1}_{i+1,j}
    -T^{n+1}_{ij}}{\Delta_i}\\
  -\beta_{i,j-1/2} \frac{T^{n+1}_{ij}
    -T^{n+1}_{i,j-1}}{\Delta_j} +\beta_{i,j+1/2} \frac{T^{n+1}_{i,j+1}
    -T^{n+1}_{i,j}}{\Delta_j}\:.
  \label{eq:conduction_fv_multline}
\end{multline}

@@

Rearranging for temperature, we can then form a system of equations
amenable to matrix solutions, not yet considering boundary conditions:

\begin{multline}
 \Big[1 + \frac{\alpha_{ij}}{\Delta_i}(\beta_{i-1/2,j} +
   \beta_{i+1/2,j} + \beta_{i,j-1/2} + \beta_{i,j+1/2})\Big]
 T^{n+1}_{ij} \\
 + \Big[-\frac{\alpha_{ij}}{\Delta_i}
   \beta_{i-1/2,j}\Big] T^{n+1}_{i-1,j}
 + \Big[-\frac{\alpha_{ij}}{\Delta_i} \beta_{i+1/2,j}\Big]
 T^{n+1}_{i+1,j} \\
 + \Big[-\frac{\alpha_{ij}}{\Delta_j}
   \beta_{i,j-1/2}\Big] T^{n+1}_{i,j-1} +
 \Big[-\frac{\alpha_{ij}}{\Delta_j} \beta_{i,j+1/2}\Big]
 T^{n+1}_{i,j+1} = T^n_{ij}\:.
 \label{eq:conduction_inner_terms}
\end{multline}

Finally, we consider cell-centered thermal conductivity values as a
single material occupies an entire cell:

\begin{equation}
  \beta_{i-1/2,j} = \frac{\beta_{ij}+\beta_{i-1,j}}{2}
  \label{eq:conduction_conductivity}
\end{equation}

Applying Eq.~(\ref{eq:conduction_conductivity}), we arrive at the discrete,
time-dependent conduction equation:

\begin{multline}
 \Big[1 + \frac{\alpha_{ij}}{2\Delta_i}(\beta_{i-1,j} +
   \beta_{i+1,j} + 4 \beta_{i,j} + \beta_{i,j-1} + \beta_{i,j+1})\Big]
 T^{n+1}_{ij} \\
 + \Big[-\frac{\alpha_{ij}}{2 \Delta_i}
   (\beta_{i-1,j}+\beta_{ij})\Big] T^{n+1}_{i-1,j}
 + \Big[-\frac{\alpha_{ij}}{2 \Delta_i}(\beta_{ij}+\beta_{i+1,j})\Big]
 T^{n+1}_{i+1,j} \\
 + \Big[-\frac{\alpha_{ij}}{2 \Delta_j}
   (\beta_{i,j-1}+\beta_{ij})\Big] T^{n+1}_{i,j-1} +
 \Big[-\frac{\alpha_{ij}}{2 \Delta_j}(\beta_{ij}+\beta_{i,j+1})\Big]
 T^{n+1}_{i,j+1} = T^n_{ij}\:.
 \label{eq:conduction_discrete_equation}
\end{multline}
